---
title: "R Notebook"
output: html_notebook
---
library(curl)
library(Rmisc)
library(ggplot2)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)



1. Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education). NOTE: You will not want to use the built in var() and sd() commands as these are for samples.

```{r}

height_sum <- summarySE(data = d, measurevar = "height")
height_sum
weight_sum <- summarySE(data = d, measurevar = "weight")
weight_sum
kill_sum <- summarySE(data = d, measurevar = "zombies_killed")
kill_sum
educate_sum <- summarySE(data = d, measurevar = "years_of_education")
educate_sum
age_sum <- summarySE(data = d, measurevar = "age")
age_sum

```


2. Use {ggplot} to make boxplots of each of these variables by gender.

```{r}

ggplot(data = d, aes(x = gender, y = height)) +
  geom_boxplot(color="red", fill = "green")
 
ggplot(data = d, aes(x = gender, y = weight)) +
  geom_boxplot(color="coral", fill="black")

ggplot(data = d, aes(x = gender, y = zombies_killed)) +
  geom_boxplot()
  
ggplot(data = d, aes(x = gender, y = years_of_education)) +
  geom_boxplot()

ggplot(data = d, aes(x = gender, y = age)) +
  geom_boxplot()

```

3. Use {ggplot} to make scatterplots of height and weight in relation to age. Do these variables seem to be related? In what way?

```{r}

ggplot(data = d, aes(x = age, y = height)) +
  geom_point() + geom_smooth(method = lm)

ggplot(data = d, aes(x = age, y = weight)) +
  geom_point() + geom_smooth(method = lm)

# Yes both height and weight seem to be positivly coorelated with age
```


4. Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not normal, can you determine from which common distribution they are drawn?

```{r}

hist(d$height)
qqnorm(d$height)
qqline(d$height)

# Height seems to follow a normal distribution

hist(d$weight)
qqnorm(d$weight)
qqline(d$weight)

# Weight seems to follow a normal distribution

hist(d$age)
qqnorm(d$age)
qqline(d$age)

# Age follows a normal distribution

hist(d$zombies_killed)
qqnorm(d$zombies_killed)
qqline(d$zombies_killed)

# Zombies killed does not follow a normal distribution
#It looks like a binomial distribution

hist(d$years_of_education)
qqnorm(d$years_of_education)
qqline(d$years_of_education)

# Years of education does not follow a normal distribution
# It looks like a binomial distribution


```


5. Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable, and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you may need to base your estimate of the CIs on slightly different code than for the normal…

```{r}

s_height <- sample(d$height, size = 30, replace = FALSE)
m_height <- mean(s_height)
m_height
sd_height <- sd(s_height)
sd_height
sem_height <- sd(s_height)/sqrt(length(s_height))
sem_height
lower_height <- m_height - qt(1 - 0.05/2, df = 30 - 1) * sem_height 
upper_height <- m_height + qt(1 - 0.05/2, df = 30 - 1) * sem_height 
ci_t_height <- c(lower_height, upper_height)
ci_t_height

s_weight <- sample(d$weight, size = 30, replace = FALSE)
m_weight <- mean(s_weight)
m_weight
sd_weight <- sd(s_weight)
sd_weight
sem_weight <- sd(s_weight)/sqrt(length(s_weight))
sem_weight
lower_weight <- m_weight - qt(1 - 0.05/2, df = 30 - 1) * sem_weight 
upper_weight <- m_weight + qt(1 - 0.05/2, df = 30 - 1) * sem_weight 
ci_t_weight <- c(lower_weight, upper_weight)
ci_t_weight

s_age <- sample(d$age, size = 30, replace = FALSE)
m_age <- mean(s_age)
m_age
sd_age <- sd(s_age)
sd_age
sem_age <- sd(s_age)/sqrt(length(s_age))
sem_age
lower_age <- m_age - qt(1 - 0.05/2, df = 30 - 1) * sem_age 
upper_age <- m_age + qt(1 - 0.05/2, df = 30 - 1) * sem_age 
ci_t_age <- c(lower_age, upper_age)
ci_t_age

?qbinom

s_zombies_killed <- sample(d$zombies_killed, size = 30, replace = FALSE)
m_zombies_killed <- mean(s_zombies_killed)
m_zombies_killed
sd_zombies_killed <- sd(s_zombies_killed)
sd_zombies_killed
sem_zombies_killed <- sd(s_zombies_killed)/sqrt(length(s_zombies_killed))
sem_zombies_killed

# qbinom not working

lower_zombies_killed <- m_zombies_killed - qbinom(1 - 0.05/2, df = 30 - 1) * sem_zombies_killed 
upper_zombies_killed <- m_zombies_killed + qbinom(1 - 0.05/2, df = 30 - 1) * sem_zombies_killed 
ci_t_zombies_killed <- c(lower_zombies_killed, upper_zombies_killed)
ci_t_zombies_killed

s_years_of_education <- sample(d$years_of_education, size = 30, replace = FALSE)
m_years_of_education <- mean(s_years_of_education)
m_years_of_education
sd_years_of_education <- sd(s_years_of_education)
sd_years_of_education
sem_years_of_education <- sd(s_years_of_education)/sqrt(length(s_years_of_education))
sem_years_of_education

# qbinom not working

lower_years_of_education <- m_years_of_education - qbinom(1 - 0.05/2, df = 30 - 1) * sem_years_of_education 
upper_years_of_education <- m_years_of_education + qbinom(1 - 0.05/2, df = 30 - 1) * sem_years_of_education 
ci_t_years_of_education <- c(lower_years_of_education, upper_years_of_education)
ci_t_years_of_education


```


6. Now draw 99 more random samples of 30 zombie apocalypse survivors, and calculate the mean for each variable for each of these samples. Together with the first sample you drew, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of this distribution of means for each variable? How do the standard deviations of means compare to the standard errors estimated in [5]? What do these sampling distributions look like (a graph might help here)? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution?

```{r}
x_height <- NULL
for (i in 1:99) {
  x_height[i] <- mean(sample(d$height, size = 30, replace = FALSE)) 
}
all_height <- c(m_height, x_height)
m_all_height <- mean(all_height)
m_all_height
sd_all_height <- sd(all_height)
sd_all_height

# The standard deviation here is very similar to the standard error in the last step

hist(all_height)

# The distribution looks normal

x_weight <- NULL
for (i in 1:99) {
  x_weight[i] <- mean(sample(d$weight, size = 30, replace = FALSE)) 
}
all_weight <- c(m_weight, x_weight)
m_all_weight <- mean(all_weight)
m_all_weight
sd_all_weight <- sd(all_weight)
sd_all_weight

# The standard deviation here is very similar to the standard error in the last step

hist(all_weight)

# The distribution looks normal

x_age <- NULL
for (i in 1:99) {
  x_age[i] <- mean(sample(d$age, size = 30, replace = FALSE)) 
}
all_age <- c(m_age, x_age)
m_all_age <- mean(all_age)
m_all_age
sd_all_age <- sd(all_age)
sd_all_age

# The standard deviation here is very similar to the standard error in the last step

hist(all_age)

# The distribution looks normal

x_zombies_killed <- NULL
for (i in 1:99) {
  x_zombies_killed[i] <- mean(sample(d$zombies_killed, size = 30, replace = FALSE)) 
}
all_zombies_killed <- c(m_zombies_killed, x_zombies_killed)
m_all_zombies_killed <- mean(all_zombies_killed)
m_all_zombies_killed
sd_all_zombies_killed <- sd(all_zombies_killed)
sd_all_zombies_killed

# The standard deviation here is very similar to the standard error in the last step

hist(all_zombies_killed)

# The distribution looks normal

x_years_of_education <- NULL
for (i in 1:99) {
  x_years_of_education[i] <- mean(sample(d$years_of_education, size = 30, replace = FALSE)) 
}
all_years_of_education <- c(m_years_of_education, x_years_of_education)
m_all_years_of_education <- mean(all_years_of_education)
m_all_years_of_education
sd_all_years_of_education <- sd(all_years_of_education)
sd_all_years_of_education

# The standard deviation here is very similar to the standard error in the last step

hist(all_years_of_education)

# The distribution looks normal

```

